Exploration

### 2018-03-06 exploration.Rmd
shifting step size multiplication

  #---- Truth: use assigned slopes to fill IPM matrix
  ### growth and survival
  G.mx <- h*outer(y, y, calc_grow, p=p, n_gz=n_gz, X.g=X_g[i,])
  S.v <- calc_surv(y, p=p, n_sz=n_sz, X.s=X_s[i,])
  ### Fix eviction of individuals below/above size limits
  for(k in 1:(n/2)) G.mx[1,k] <- G.mx[1,k] + 1 - sum(G.mx[,k])
  for(k in (n/2+1):n) G.mx[n,k] <- G.mx[n,k] + 1 - sum(G.mx[,k])
  ### fill P and F matrices
  for(k in z.i) Ps[k,z.i,i] <- G.mx[k-1,]*S.v
  Ps[1,1,i] <- calc_staySB(p)
  ### store seed production
  Fb[z.i,z.i,i] <- outer(y, y, calc_rcrDir, p=p, n_seedz=n_seedz, n_flz=n_flz, 
                         X.seed=X_seed[i,], X.fl=X_fl[i,])
  Fb[1,z.i,i] <- calc_addSB(y, p=p, n_seedz=n_seedz, n_flz=n_flz, 
                            X.seed=X_seed[i,], X.fl=X_fl[i,])
  Fs[z.i,z.i,i] <- h * (1 - p$p_emig) * Fb[z.i,z.i,i]
  Fs[1,z.i,i] <- (1 - p$p_emig) * Fb[1,z.i,i]
  Fs[z.i,1,i] <- calc_rcrSB(y, p)

@@

  #---- Truth: add immigrants
  sdd.j <- which(sdd[,,2,]==sdd.i, arr.ind=TRUE)
  p.ij <- sdd[,,1,][sdd.j]
  Fs[z.i,z.i,i] <- Fs[z.i,z.i,i] + 
    h * Reduce(`+`, map2(sdd.j[,3], p$p_emig*p.ij, ~(Fb[z.i,z.i,.x] * .y)))
  Fs[1,z.i,i] <- Fs[1,z.i,i] + Fb[1,z.i,sdd.j[,3]] %*% (p$p_emig*p.ij)

>>>>

  #---- Truth: use assigned slopes to fill IPM matrix
  ### growth and survival
  G.mx <- h*outer(y, y, calc_grow, p=p, n_gz=n_gz, X.g=X_g[i,])
  S.v <- calc_surv(y, p=p, n_sz=n_sz, X.s=X_s[i,])
  ### Fix eviction of individuals below/above size limits
  for(k in 1:(n/2)) G.mx[1,k] <- G.mx[1,k] + 1 - sum(G.mx[,k])
  for(k in (n/2+1):n) G.mx[n,k] <- G.mx[n,k] + 1 - sum(G.mx[,k])
  ### fill P and F matrices
  for(k in z.i) Ps[k,z.i,i] <- G.mx[k-1,]*S.v
  Ps[1,1,i] <- calc_staySB(p)
  ### store seed production
  Fb[z.i,z.i,i] <- h * outer(y, y, calc_rcrDir, p=p, n_seedz=n_seedz, n_flz=n_flz, 
                         X.seed=X_seed[i,], X.fl=X_fl[i,])
  Fb[1,z.i,i] <- h * calc_addSB(y, p=p, n_seedz=n_seedz, n_flz=n_flz, 
                            X.seed=X_seed[i,], X.fl=X_fl[i,])
  Fs[z.i,z.i,i] <- (1 - p$p_emig) * Fb[z.i,z.i,i]
  Fs[1,z.i,i] <- (1 - p$p_emig) * Fb[1,z.i,i]
  Fs[z.i,1,i] <- calc_rcrSB(y, p)

@@

  #---- Truth: add immigrants
  sdd.j <- which(sdd[,,2,]==sdd.i, arr.ind=TRUE)
  p.ij <- sdd[,,1,][sdd.j]
  Fs[z.i,z.i,i] <- Fs[z.i,z.i,i] + 
    Reduce(`+`, map2(sdd.j[,3], p$p_emig*p.ij, ~(Fb[z.i,z.i,.x] * .y)))
  Fs[1,z.i,i] <- Fs[1,z.i,i] + Fb[1,z.i,sdd.j[,3]] %*% (p$p_emig*p.ij)
